XS-Face: Merge Raw Data

### 2021-03-15 analysis/1_merge_data/merge_all_data.Rmd
amend details to cameras in preprocessing

### Load demographics
```{r}
# All of the videos were filmed with an MD-80 headcam. Some videos had a fisheye lens attached to them that increased their FOV by approximately 50% in both directions (see manuscript; in demographics column "fisheye"). This was determined by looking at the third-person videos.

@@

### Sanity checks for merging detectors
We know that openPose works on videos and so might notget all frames. Let's check out the frames it doesn't have

>>>>

### Load demographics
```{r}
# Some of the videos were filmed with an MD-80 headcam where a fisheye lens attached to them that increased their FOV by approximately 50% in both directions (see manuscript; in demographics column "fisheye"). This was determined by looking at the third-person videos.

@@

### Sanity checks for merging detectors
We know that openPose works on videos and so might not get all frames. Let's check out the frames it doesn't have
